### 2016-07-06 intro.tex
cheers

\heading{Related work: constructions}
\begin{itemize}
\item Bellovin and Cheswick, ``Privacy-Enhanced Searches Using Encrypted Bloom Filters''.
\item Kerschbaum , ``Public-Key Encrypted Bloom Filters with Applications to Supply Chain Integrity''.
\item S\"{a}rell\"{a} et al., ``BloomCasting: Security in Bloom Filter Based Multicast''.
\item Dong, Chen, Wen, ``When Private Set Intersection Meets Big Data: An Efficient and Scaleable Protocol'' \tsnote{``garbled bloom filters'', which actually store the set element by storing~$k$ xor-shares, one at each of the~$k$ hash indices (with care for reusing shares if hash collisions occur), and``oblivious bloom intersection''}\tsnote{If the filter and the hash functions are public, there is a naive attack that works for some interesting parameters.  Pick~$k$ positions $i_1,i_2,\ldots,i_k$, xor strings at these positions to get a candidate~$x$.   If $h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k$ then either $x \in S$ or~$x$ is a false-positive. (You don't have to do all~$k$ hashes, you can stop as soon as one fails to match the index.)  Say you have a 1000-position filter ($m=1000$) and a 100-element set ($n=100$), and you are willing to tolerate a 1\% FP rate.  Then you'd set $k=4$ (a la Squid).  There are roughly $2^{35}$ subsets of 4 indices to consider, which is reasonable on a laptop these days.  (Also, since $n=100$ the expected number of trials is roughly $2^{28}$.)  With the FP rate of 1\%, if you find a winner then almost certainly it is in the set.  Granted, this attack is naive, but notice that you \emph{cannot} mount it against a standard Bloom filter. Also notice that this attack might be significantly more efficient than brute force guessing over the universe of inputs (imagine that $U=\bits^{64}$), even if you know that the distribution deviates significantly from uniform. }
\item Tarkoma, Rothenberg, Lagerspetz ``Theory and Practice of Bloom Filters in Distributed Systems'' \tsnote{Great high-level coverage.  Only found preprint version though.}
\item Durham, Kantarcioglu, Xue, Kuzu, Malin ``Composite Bloom Filters for Secure Record Linkage'' \tsnote{Per-field BFs, sampled and composed into single BF that is then permuted by a secret random permtation.  No clear statement of the problem that is being solved.  Should pull full version and get details.}
\end{itemize}

>>>>

\heading{Related work: constructions}
\begin{itemize}
\item Bellovin and Cheswick, ``Privacy-Enhanced Searches Using Encrypted Bloom Filters''.
\item Kerschbaum , ``Public-Key Encrypted Bloom Filters with Applications to Supply Chain Integrity''.
\item S\"{a}rell\"{a} et al., ``BloomCasting: Security in Bloom Filter Based Multicast''.
\item Dong, Chen, Wen, ``When Private Set Intersection Meets Big Data: An Efficient and Scaleable Protocol'' \tsnote{``garbled bloom filters'', which actually store the set element by storing~$k$ xor-shares, one at each of the~$k$ hash indices (with care for reusing shares if hash collisions occur); also and``oblivious bloom intersection''}\tsnote{If the filter and the hash functions are public, there is a naive attack that works for some interesting parameters.  Pick~$k$ positions $i_1,i_2,\ldots,i_k$, xor strings at these positions to get a candidate~$x$.  If $h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k$ then either $x \in S$ or~$x$ is a false-positive. (You don't have to do all~$k$ hashes, you can stop as soon as one fails to match the index.) Say you have a 1000-position filter ($m=1000$) and a 100-element set ($n=100$), and you are willing to tolerate a 1\% FP rate.  Then you'd set $k=4$ (a la Squid).  There are roughly $2^{35}$ subsets of 4 indices to consider, which is reasonable on a laptop these days.  (Also, since $n=100$ the expected number of trials is roughly $2^{28}$.) With the FP rate of 1\%, if you find a winner then almost certainly it is in the set.  Granted, this attack is naive, but notice that you \emph{cannot} mount it against a standard Bloom filter. Also notice that this attack might be significantly more efficient than brute force guessing over the universe of inputs (imagine that $U=\bits^{64}$), even if you know that the distribution deviates significantly from uniform. }
\item Tarkoma, Rothenberg, Lagerspetz ``Theory and Practice of Bloom Filters in Distributed Systems'' \tsnote{Great high-level coverage.  Only found preprint version though.}
\item Durham, Kantarcioglu, Xue, Kuzu, Malin ``Composite Bloom Filters for Secure Record Linkage'' \tsnote{Per-field BFs, sampled and composed into single BF that is then permuted by a secret random permtation.  No clear statement of the problem that is being solved.  Should pull full version and get details.}
\end{itemize}
